---
title: "p8105_HW1_ntk2109_markdown"
author: Noah Kreski
Date: September 21, 2018
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library (tidyverse)
```
Problem 1 - Creating a data frame comprised of:

A random sample of size 10 from a uniform [0,5] distribution

A logical vector indicating whether elements of the sample are greater than 2

A (length-10) character vector

A (length-10) factor vector


```{r problem_one}
set.seed(1)

question_one_df = tibble(
  uniform_samp = runif(10, 0, 5),
  logical_vec_one = c((uniform_samp)>2),
  character_vec_one = c("This", "is", "a", "character", "vector", "that", "has", "length", "of", "ten"),
  factor_vec_one = c("male", "female","male", "female","male", "female","male", "female","male", "female")
)

```

The mean of the random sample is `r mean(question_one_df$uniform_samp)`.
The mean of the logical vector is `r mean(question_one_df$logical_vec_one)`.
The mean of the character vector is `r mean(question_one_df$character_vec_one)`.
The mean of the factor vector is `r mean(question_one_df$factor_vec_one)`.