---
title: "p8105_HW1_ntk2109_markdown"
author: Noah Kreski
Date: September 21, 2018
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library (tidyverse)
```
##1A. Question One, vectors

Problem 1 - Creating a data frame comprised of:

A random sample of size 10 from a uniform [0,5] distribution

A logical vector indicating whether elements of the sample are greater than 2

A (length-10) character vector

A (length-10) factor vector


```{r problem_one_a}
set.seed(1)

question_one_df = tibble(
  uniform_samp = runif(10, 0, 5),
  logical_vec_one = c((uniform_samp)>2),
  character_vec_one = c("This", "is", "a", "character", "vector", "that", "has", "length", "of", "ten"),
  factor_vec_one = factor(c("male", "female","male", "female","male", "female","male", "female","male", "female")
))

```

The mean of the random sample is `r mean(question_one_df$uniform_samp)`.

The mean of the logical vector is `r mean(question_one_df$logical_vec_one)`.

The mean of the character vector is `r mean(question_one_df$character_vec_one)`.

The mean of the factor vector is `r mean(question_one_df$factor_vec_one)`.

For the random sample and logical vector, means were produced. For the character vector and factor vector, no means were produced.

##B. Conversion to numeric

```{r problem_one_b}
question_one_numeric_df = tibble(
  logical_vec_one_numeric = as.numeric(question_one_df$logical_vec_one),
  character_vec_one_numeric = as.numeric(question_one_df$character_vec_one),
  factor_vec_one_numeric =  as.numeric(question_one_df$factor_vec_one)
)

```

The new mean of the logical vector is `r mean(question_one_numeric_df$logical_vec_one_numeric)`.

The new mean of the character vector is `r mean(question_one_numeric_df$character_vec_one_numeric)`.

The new mean of the factor vector is `r mean(question_one_numeric_df$factor_vec_one_numeric)`.

Now, both the logical and factor vectors produce mean values, whereas the character vector is incapable of being converted this way.

##C. Double conversion of factor and character vectors

```{r problem_one_c}
double_conversion_df = tibble(
  character_vec_one_double = as.numeric(factor(c(question_one_df$character_vec_one))),
  factor_vec_one_double =  as.numeric(as.character(question_one_df$factor_vec_one))
)

```

The new mean of the character vector is `r mean(double_conversion_df$character_vec_one_double)`.

The new mean of the factor vector is `r mean(double_conversion_df$factor_vec_one_double)`.

It appears that converting from a character vector to a factor vector to a numeric one will allow for the computation of a mean, but converting from factor to character to numeric produces issues, just as seen in part b when converting from character to numeric.

##2A. Data Frame for random sample, description of vector

Creating a data frame comprised of:

x: a random sample of size 1000 from a standard Normal distribution

y: a random sample of size 1000 from a standard Normal distribution

A logical vector indicating whether the x + y > 0

A numeric vector created by coercing the above logical vector

A factor vector created by coercing the above logical vector

```{r problem_two_a}
set.seed(1)
random_df = tibble(
  x = rnorm(1000),
  y = rnorm(1000),
  random_logical = c((x+y)>0),
  random_numeric = as.numeric(random_logical),
  random_factor =factor(c(random_logical))
)

```

The above code produces vectors with the following characteristics:

The size of the data set is `r nrow(random_df)` observations with `r ncol(random_df)` variables for each.

The mean of x is `r mean(random_df$x)` and the median is `r median(random_df$x)`.

The proportion of cases for which the logical vector is true is `r mean(random_df$random_numeric)`.
