---
title: "p8105_HW1_ntk2109_markdown"
author: Noah Kreski
Date: September 21, 2018
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library (tidyverse)
```
##A. Question One, vectors

Problem 1 - Creating a data frame comprised of:

A random sample of size 10 from a uniform [0,5] distribution

A logical vector indicating whether elements of the sample are greater than 2

A (length-10) character vector

A (length-10) factor vector


```{r problem_one_a}
set.seed(1)

question_one_df = tibble(
  uniform_samp = runif(10, 0, 5),
  logical_vec_one = c((uniform_samp)>2),
  character_vec_one = c("This", "is", "a", "character", "vector", "that", "has", "length", "of", "ten"),
  factor_vec_one = factor(c("male", "female","male", "female","male", "female","male", "female","male", "female")
))

```

The mean of the random sample is `r mean(question_one_df$uniform_samp)`.

The mean of the logical vector is `r mean(question_one_df$logical_vec_one)`.

The mean of the character vector is `r mean(question_one_df$character_vec_one)`.

The mean of the factor vector is `r mean(question_one_df$factor_vec_one)`.

For the random sample and logical vector, means were produced. For the character vector and factor vector, no means were produced.

##B. Conversion to numeric

```{r problem_one_b}
question_one_numeric_df = tibble(
  logical_vec_one_numeric = as.numeric(question_one_df$logical_vec_one),
  character_vec_one_numeric = as.numeric(question_one_df$character_vec_one),
  factor_vec_one_numeric =  as.numeric(question_one_df$factor_vec_one)
)

```

The new mean of the logical vector is `r mean(question_one_numeric_df$logical_vec_one_numeric)`.

The new mean of the character vector is `r mean(question_one_numeric_df$character_vec_one_numeric)`.

The new mean of the factor vector is `r mean(question_one_numeric_df$factor_vec_one_numeric)`.

Now, both the logical and factor vectors produce mean values, whereas the character vector is incapable of being converted this way.

##C. Double conversion of factor and character vectors

```{r problem_one_c}
double_conversion_df = tibble(
  character_vec_one_double = as.numeric(factor(c(question_one_df$character_vec_one))),
  factor_vec_one_double =  as.numeric(as.character(question_one_df$factor_vec_one))
)

```

The new mean of the character vector is `r mean(double_conversion_df$character_vec_one_double)`.

The new mean of the factor vector is `r mean(double_conversion_df$factor_vec_one_double)`.

It appears that converting from a character vector to a factor vector to a numeric one will allow for the computation of a mean, but converting from factor to character to numeric produces issues, just as seen in part b when converting from character to numeric.